---
title: "AWE workflow"
author: "Evan L Ray, Nicholas G Reich, Stephen A Lauer"
date: "April 4, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
# devtools::install_github("krlmlr/here")
knitr::opts_knit$set(root.dir = here::here())
```

## Setup

To run this code, you will need to install the following package from github:

```{r github-packages}
devtools::install_github("reichlab/kcde")
```

If you are running this on a Mac and get an error that looks like:

```
ld: warning: directory not found for option '-L/usr/local/lib/gcc/x86_64-apple-darwin13.0.0/4.8.2'
ld: library not found for -lgfortran
```

Then you may have a wrong version of `gfortran`.
Try running the following in the Terminal:

```
curl -O http://r.research.att.com/libs/gfortran-4.8.2-darwin13.tar.bz2
sudo tar fvxj gfortran-4.8.2-darwin13.tar.bz2 -C /8
```

If `kcde` still does not install, you may have too recent a version of `gfortran` and you may need to uninstall your current version with a program such as `homebrew`.

```
brew uninstall gcc
```

## Data Processing

Download the data from the CDC and clean it, save as `data-raw/allflu-cleaned.csv` and `data/flu_data.rdata`.
The version in this repository was created on February 17, 2017 and covers flu data through the last week of 2016.

```{r data-processing}
source("inst/data-processing/create-clean-flu-data.R")
```

Find the regional means from 1997-2006 and save those as a baseline.
Saved in `data-raw/cdc-baselines.csv` and `data/flu_onset_baselines.rdata`.

```{r make-baselines}
source("inst/data-processing/create-clean-flu-data.R")
```

## Model Estimation
### KDE

Estimate KDE fits for Leave-One-Season-Out (LOSO) cross validation, which are saved in `inst/estimation/kde/fits`.
Also makes LOSO predictions, which are saved in `inst/estimation/loso-predictions`. 
This file also sources a script that quickly creates diagnostic figures for checking the model fits.

```{r kde-fit}
source("estimation/kde/kde-estimation.R")
```

`inst/estimation/kde/check-loso-predictions.R` runs a more thorough set of diagnostics and creates multiple pdfs of figures for checking the model fits and predictions.

```{r kde-diagnostics}
source("inst/estimation/kde/check-loso-predictions.R")
```

### KCDE

Estimate the KCDE fits on the cluster, save them in `inst/estimation/kcde/fits`.

```{r fit-kcde}
source("inst/estimation/kcde/submit-cluster-job-kcde-estimation-step.R")
```

Run LOSO cross validation on the cluster and save results to `inst/estimation/loso-predictions`.

```{r kcde-loso}
source("inst/estimation/kcde/submit-cluster-job-kcde-loso-prediction-step.R")
```

Estimate copulas for LOSO cross validation and save results to `inst/estimation/kcde/copula-fits`.

```{r kcde-copulas}
source("inst/estimation/kcde/copula-estimation-step.R")
source("inst/estimation/kcde/copula-estimation-step-none-left-out.R")
```

Check that the distributions sum to 1 and print pdfs of model diagnostics.

```{r kcde-diagnostics}
source("inst/estimation/kcde/check_dists_sum_to_1.R")
source("inst/estimation/kcde/check-loso-predictions.R")
```

### SARIMA

Fit the LOSO SARIMA models using `auto.arima()` and save the fits in `inst/estimation/sarima/fits`

```{r sarima-fit}
source("inst/estimation/sarima/sarima-estimation-loso.R")
```

Make LOSO SARIMA predictions on the cluster and save in `inst/estimation/loso-predictions`.

```{r sarima-loso}
source("inst/estimation/sarima/submit-cluster-job-sarima-loso-prediction-step.R")
```

Make diagnostic plots for SARIMA predictions.

```{r sarima-diagnostics}
source("inst/estimation/sarima/check-loso-predictions.R")
```

## Ensemble Weight Estimation

### EM algorithm

Estimate the weights for the degenerate EM stacking algorithm, as specified in this presentation (http://www.cs.cmu.edu/~roni/11761-f16/Presentations/degenerateEM.pdf).
Fitted weights are saved in `inst/estimation/em-stacking/fits`.

```{r em-fit}
source("inst/estimation/em-stacking/em-stacking-estimation.R")
```