---
title: "AWE workflow"
author: "Evan L Ray, Nicholas G Reich, Stephen A Lauer"
date: "April 4, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# devtools::install_github("krlmlr/here")
knitr::opts_knit$set(root.dir = here::here())
```

## Data Processing

Download the data from the CDC and clean it, save as "data-raw/allflu-cleaned.csv" and "data/flu_data.rdata". The version in this repository was created on February 17, 2017 and covers flu data through the last week of 2016.

```{r data-processing, eval=FALSE}
source("inst/data-processing/create-clean-flu-data.R")
```

Find the regional means from 1997-2006 and save those as a baseline. Saved in "data-raw/cdc-baselines.csv" and  = "data/flu_onset_baselines.rdata".

```{r make-baselines, eval=FALSE}
source("inst/data-processing/create-clean-flu-data.R")
```

## Estimation

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
